Honey Bees - DESeq

### 2018-04-11 VirusHoneyBee/DESeq2/Method1/makeDataMetrics.Rmd
Fix Standard Cluster Limma and edgeR

    allPairs = rbind(allPairs, data.frame(Treatment1 = uTreat[i], Treatment2 = uTreat[j], NumberDEG = degLength, Treatment1Larger = t1Length, Treatment2Larger = t2Length))
  }
}
allPairs <- allPairs[order(allPairs$NumberDEG),]
allPairs
saveRDS(dataMetrics, file="dataMetrics.Rds")
```

>>>>

    allPairs = rbind(allPairs, data.frame(Treatment1 = uTreat[i], Treatment2 = uTreat[j], NumberDEG = degLength, Treatment1Larger = t1Length, Treatment2Larger = t2Length))
  }
}
allPairs <- allPairs[order(allPairs$NumberDEG),]
allPairs
saveRDS(data, file="data.Rds")
saveRDS(dataMetrics, file="dataMetrics.Rds")
```
